I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-04-27 lipics-master/comppaths.tex
Add files via upload
update

We then partition the set of neurons in hidden layers: 
\begin{enumerate}
	\item $B_{zero}= \{n \mid \forall \text{ path $\rho$ from $n$ to } z, weight(\rho)=0\}$.
	\item $B_{open}$ is the set of neurones reachable with $>0$ weight from $A_{open}$ and such that there is at least one path to $z$ with non zero weight.
	\item $B_{pure}$ is the set of remaining neurons.
\end{enumerate}

>>>>

We then partition the set of neurons in hidden layers: 
\begin{enumerate}
	\item $B_{zero}= \{n \mid \forall \text{ path $\rho$ from $n$ to } z, weight(\rho)=0\}$.
	\item $B_{open}$ is the set of neurons reachable with $>0$ weight from $A_{open}$ and such that there is at least one path to $z$ with non zero weight.
	\item $B_{pure}$ is the set of remaining neurons.
\end{enumerate}

### 2024-04-27 lipics-master/proofs.tex
Add files via upload
update

{\color{red}Notice that above definitions only involve weights, and do not use bias. As demonstrated by the following lemmas and proofs, our discussion is independent of bias, regardless of whether the bias values are very large or very small.}

@@

{\color{red} As we mentioned earlier, this proof does not have any requirements on the bias.}

@@

		{ \color{red}	Similarly, above definitions $A_{zero},A_{open}, A_{pure}$ and $B_{zero},B_{open},B_{pure}$ do not consider bias, and any kind of bias will not affect our theorem.}

@@

{\color{red} In all the statements and proofs above, we do not make any assumptions about bias, and bias will not affect our discussion. }

@@

We now prove Theorem \ref{th2} under the fairly light {\em well-connected hypothesis} (H1) that the DNN is such that for every 2 (not necessarily disjoint) paths $\rho_1,\rho_2$ with non-zero weight with the same source $m$ and the same target $n$ at least 2 layers apart, there exists another path $\rho_3$ from $m$ to $n$ (with non zero-weight) totally disjoint from $\rho_1$ and $\rho_2$ (except at the source and target). This hypothesis is used to remove corner cases which will not happen in actual DNNs, which all are well-connected. {\color{red} Moreover, this hypothesis only matters in the theoretical proof. This is because in practice, paths with zero or very small weights will have very small effect on the output, and very small effect on the models, too.  Usually these paths will not be considered.}

>>>>

{Notice that above definitions only involve weights, and do not use bias. As demonstrated by the following lemmas and proofs, our discussion is independent of bias, regardless of whether the bias values are very large or very small.}

@@

{ As we mentioned earlier, this proof does not have any requirements on the bias.}

@@

		{ 	Similarly, above definitions $A_{zero},A_{open}, A_{pure}$ and $B_{zero},B_{open},B_{pure}$ do not consider bias, and any kind of bias will not affect our theorem.}

		\begin{figure}[h]
			\centering
			\begin{tikzpicture}[>=stealth, node distance=2cm]
				% Input nodes (two types)
				\node[circle, draw, minimum size=0.5cm] (input1) at (-1,0) {$a_0$};
				\node[circle, draw, minimum size=0.5cm] (input2) at (-2,0) {$a_1$};
				\node[circle, draw, minimum size=0.5cm] (input3) at (-4,0) {$a_2$};

				\node[circle, draw, minimum size=0.5cm] (input4) at (-5,0) {$a_3$};
				\node[circle, draw, minimum size=0.5cm] (input5) at (-7,0) {$a_4$};
				\node[circle, draw, minimum size=0.5cm] (input6) at (-8,0) {$a_5$};

				\draw[draw=black, dashed] (-1.5,0) ellipse (1.35 and 0.75);
				\node[below] at (-1.5,-0.75) {$A_{zero}$};

				\draw[draw=black, dashed] (-2,2) ellipse (0.75 and 0.75);
				\node[right] at (-1,2) {$B_{zero}$};

				% Hidden layer nodes

				\node[circle, draw, minimum size=0.5cm, fill=blue!20] (hidden1) at (-2,2) {$n_0$};

				\node[circle, draw, minimum size=0.5cm, fill=blue!20] (hidden2) at (-4,2) {$n_1$};
				\node[circle, draw, minimum size=0.5cm, fill=blue!20] (hidden3) at (-5,2) {$n_2$};

				\node[circle, draw, minimum size=0.5cm, fill=blue!20] (hidden4) at (-7,2) {$n_3$};
				\node[circle, draw, minimum size=0.5cm, fill=blue!20] (hidden5) at (-8,2) {$n_4$};

				\draw[draw=black, dashed] (-4.5,0) ellipse (1.35 and 0.75);
				\node[below] at (-4.5,-0.75) {$A_{pure}$};

				\draw[draw=black, dashed] (-7.5,0) ellipse (1.35 and 0.75);
				\node[below] at (-7.5,-0.75) {$A_{open}$};

				\draw[draw=black, dashed] (-4.5,2) ellipse (1.35 and 0.75);
				\node[left] at (-3.5,3) {$B_{pure}$};

				\draw[draw=black, dashed] (-7.5,2) ellipse (1.35 and 0.75);
				\node[left] at (-8.5,1.5) {$B_{open}$};

				% Output node
				\node[circle, draw, minimum size=0.8cm, fill=red!20] (output) at (-5,4) {$z$};

				% connections

				\draw[->] (input1) -- (hidden1);

				\draw[->] (input3) -- (hidden5);

				\draw[->] (input4) -- (hidden4);

				%		% Connect input to hidden layer
				\foreach \i in {3,4} {
					\foreach \h in {3,2} {
						\draw[line width=1.5pt, ->] (input\i) -- (hidden\h);
					}
				}

				\foreach \i in {5,6} {
					\foreach \h in {4,5} {
						\draw[->] (input\i) -- (hidden\h);
					}
				}
				%		
				% Connect hidden layer to output
				\foreach \h in {2,3} {
					\draw[line width=1pt,->] (hidden\h) -- (output);
				}

				\foreach \h in {4,5} {
					\draw[->] (hidden\h) -- (output);
				}

				%\		% Input label
				\node[left=0.7cm of input6] {Input Layer};

				% Hidden label
				\node[left=0.7cm of hidden5] {Hidden Layer};

				% Output label
				\node[left=0.5cm of output] {Output Layer};
			\end{tikzpicture}
			\caption{Definitions in the proof of Theorem \ref{th2}}
			\label{fig:neural_network_types_simplified}
		\end{figure}

@@

{ In all the statements and proofs above, we do not make any assumptions about bias, and bias will not affect our discussion. }

@@

We now prove Theorem \ref{th2} under the fairly light {\em well-connected hypothesis} (H1) that the DNN is such that for every 2 (not necessarily disjoint) paths $\rho_1,\rho_2$ with non-zero weight with the same source $m$ and the same target $n$ at least 2 layers apart, there exists another path $\rho_3$ from $m$ to $n$ (with non zero-weight) totally disjoint from $\rho_1$ and $\rho_2$ (except at the source and target). This hypothesis is used to remove corner cases which will not happen in actual DNNs, which all are well-connected. { Moreover, this hypothesis only matters in the theoretical proof. This is because in practice, paths with zero or very small weights will have very small effect on the output, and very small effect on the models, too.  Usually these paths will not be considered.}

### 2024-04-27 lipics-master/valabstraction.tex
Add files via upload
update

An extremely efficient algorithm that alleviates some of the inacuraccies is DeepPoly \cite{deeppoly}, also independently discovered as the CROWN algorithm \cite{crown}. Instead of fixed bounds for each neuron $n$ in layer $k$, DeepPoly maintains two affine functions representing the lower and upper bounds of the neuron's value, based on inputs from the previous layer $k-1$. For instance, denote $f_i \leq x_i \leq g_i$ with, for example, $f_{3}(x_3)=f_4(x_4)=0$ and $g_3(x_3) = \frac{x_3+2}{2}$, $g_4(x_4) = \frac{x_4+2}{2}$. This leads to $x_5 \leq g_3(x_3) + 2 g_4(x_4) = \frac{x_3 + 2x_4 + 6}{2} = \frac{3x_1 - x_2 + 6}{2}\leq 5$.

>>>>

An extremely efficient algorithm that alleviates some of the inaccuracies is DeepPoly \cite{deeppoly}, also independently discovered as the CROWN algorithm \cite{crown}. Instead of fixed bounds for each neuron $n$ in layer $k$, DeepPoly maintains two affine functions representing the lower and upper bounds of the neuron's value, based on inputs from the previous layer $k-1$. For instance, denote $f_i \leq x_i \leq g_i$ with, for example, $f_{3}(x_3)=f_4(x_4)=0$ and $g_3(x_3) = \frac{x_3+2}{2}$, $g_4(x_4) = \frac{x_4+2}{2}$. This leads to $x_5 \leq g_3(x_3) + 2 g_4(x_4) = \frac{x_3 + 2x_4 + 6}{2} = \frac{3x_1 - x_2 + 6}{2}\leq 5$.
